---
title: "EAS501_week1"
author: "Bangzhao Shu"
date: "2021/10/29"
output: html_document
---
# Qestion 1 
First of all, Open data benefits because of its transparency and it is democratic controlled. All the people in society participate in creating open data, so it is also self-empowered. Second, open data improves private products and services. Third, open data improves efficiency and effectiveness of government services. Forth, open data impacts measurement of policies. Finally, it offers new knowledge from combined data sources and patterns in large data volumes. For example, a broader social science research could be undertaken with the data set put together by Obama's team for his 2008 and 2012 election campaigns. It would provide an incredibly rich social, political and economic insight into US society.  
The challenges of open data includes, the lack of new data analytics that can make sense of massive data sets; the limited access to open data which is because the data is mainly generated by private business and government; the research that just use big data to speak for themselves and doesn't use contextual and domain-specific knowledge.
# Qestion 2
First of all, we have to import all the packages required for geovisualization.
```{r}
library(tidyverse)
library(sf)
library(ggplot2)
library(ggspatial)
library(viridis)
```

Now, we have to use st_read function in package 'sf' to read the shapefile data of Boulder.
```{r}
boulder <- st_read("C:/Users/Alienware/Desktop/501_019/week1/data")
```

# Geovisualization of 

Now, we use ggplot to draw the geovisualization. we use annotation_map_tile to add a base map of the Transport Map.
the geom_sf function is for visualizing the sf data that we just created. we use Street_dis(the distance to streets) as the parameter of the aes(), to show the distance to streets of every area in boulder data. And we use scale_colour_gradient function to choose the gradient color bar that we like.
```{r}
ggplot() +
    annotation_map_tile(type = "http://b.tile2.opencyclemap.org/transport/${z}/${x}/${y}.png") +
    geom_sf(data = boulder, aes(color=Street_dis),
    fill = NA, alpha = .2) + 
    scale_colour_gradient(low = "yellow", high = "red", na.value = NA)
```

The color represents the distance to the nearest streets. Red means the distance is longer while yellow means shorter. The geovisualization shows that the central area has longer distance to streets. 
The base map is the Transport Map, which mainly shows the road network of Boulder. The base map could be a reference for the attribute of distance to the streets.

```{r}
?scale_color_gradient
```

